\documentclass[11pt]{article}
\title{\textbf{MSWL Final Project: Contribution to the OpenDaylight Community}}
\author{Sergio Arroutbi Braojos}
\usepackage{hyperref}
\date{\today}
\usepackage[bottom=14em]{geometry}
\usepackage{amsmath}
\usepackage{mathtools}

\begin{document}

\hypersetup
{   
pdfborder={0 0 0}
}
   
\maketitle

\tableofcontents

\pagebreak

\section{Introduction}
In this chapter, a brief introduction of the aim of this Final Project, the writer motivations and a short introduction to the OpenDayLight project and community will be performed.
\section{Final Project Structure \& Planification}
A short description of the Final Project structure and planification.
\subsection{Document structure}
\subsection{Final Project Agenda}
\section{Context}
On which context is this Final Project. Importance of Big Data, Cloud Computing, Software as a Service, Software Defined Network Functions Virtualization nowadays.
\subsection{Cloud Computing, SaaS \& Big Data}
\subsection{VPF}
\subsection{SDN}
\section{OpenDayLight Community}
Description of the mission of the OpenSource Project, members, licensing, project structure, leadership, community involvement and other important parameters regarding this particular community.
\subsection{Mission}
\subsection{Project Description}
\subsection{Licensing}
\subsection{Economic Aspects}
\subsection{Project Evaluation}
\subsection{Technical Architecture}
\subsection{Project Structure and Leadership}
\subsection{Participation \& Involvement}
\subsection{Channels \& Resources}
\section{Contribution}
Study of personnal skills, motivations. Proposal and implementation of different contributions to perform.
\subsection{Personal background description}
\subsection{Best Fit Collaboration Areas}
\subsection{From reader to contributor}
\section{Project achievements}
Background and feedback after contributing, level of community involvement achieved
\subsection{Community Involvement}
\subsection{Contributions}
\section{Conclussions}
A list of future works that could be performed, among those not achieved, as well as new involvement proposal.
\subsection{Future Works}
\subsection{Conclussions}
Besides this, the conclussions.
\section{Summary \& Gratitudes}
\section{Bibliography}
\end{document}
